Estimating dark matter halo concentration from the integrated mass profile

### 2015-11-01 paper/paper.tex
nuevo personaje principal

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title{A new method to estimate dark matter halo concentrations}
\author[C. Poveda, J.E. Forero-Romero, J.C. Mu\~noz-Cuartas]{
\parbox[t]{\textwidth}{\raggedright 
  C. Poveda \thanks{cn.poveda542@uniandes.edu.co}$^{1}$
  J. E. Forero-Romero \thanks{je.forero@uniandes.edu.co}$^{1}$
  J. C. Mu\~noz-Cuartas \thanks{xxxx@udea.edu.co}$^{2}$
}
\vspace*{6pt}\\
$^1$Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
No. 18A-10, Edificio Ip, Bogot\'a, Colombia\\
$^2$Instituto de F\'{\i}sica - FCEN, Universidad de Antioquia, Calle
67 No. 53-108, Medell\'{\i}n, Colombia
}

@@

We present a new method to estimate the concentration of dark matter
halos in N-body simulations.  Our method finds the concentration value
to match {\bf the} integrated mass profile as a function of halo
radius.  The main advantage of this method is that it uses the full
particle information without any binning, {\bf which makes it very
  switable in cases when resolution becomes important}. We test our
method both on mock and N-body halos to compare it against two popular
methods to find concentrations: maximum radial velocity measurements
and radial particle binning to {\bf fit the density profile}. Tests on
the mock halos show that the accuracy of our method to recover input
concentrations varies with the halo {\bf resolution}. For halos
sampled with $20$ particles our method recovers the input
concentration with $10\%$ accuracy. {\bf For the maximum radial
  velocity method it is on the order of $20\%$ while density profile
  methods perform worst at the low resolution limit since they require
  at least 200 particles inside the virial radius to make a reliable
  estimate of the density profile}. For halos with $2\times 10^4$
particles our method achieves an accuracy of $0.01\%$ while the
velocity and density profile methods achieve $0.1\%$ and $1\%$,
respectively. We measure the mass-concentration relationship on N-body
data taking care of using halos sampled with at least $200$
particles. We find that at low masses $10^{12}\hMsun <
M<10^{13}\hMsun$ our method yields median concentration values lower
by a $15\%-20\%$ compared to the velocity and density methods ({\bf
  why?}).  At higher masses $3\times 10^{13}\hMsun < M < 2\times
10^{14}\hMsun$ the three methods give similar results.
\end{abstract}

>>>>

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title{Estimating dark matter halo concentration from the integrated mass profile}
\author[C. Poveda, J.E. Forero-Romero, J.C. Mu\~noz-Cuartas]{
\parbox[t]{\textwidth}{\raggedright 
  C. Poveda \thanks{cn.poveda542@uniandes.edu.co}$^{1}$
  J. E. Forero-Romero \thanks{je.forero@uniandes.edu.co}$^{1}$
  J. C. Mu\~noz-Cuartas \thanks{xxxx@udea.edu.co}$^{2}$
}
\vspace*{6pt}\\
$^1$Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
No. 18A-10, Edificio Ip, Bogot\'a, Colombia\\
$^2$Instituto de F\'{\i}sica - FCEN, Universidad de Antioquia, Calle
67 No. 53-108, Medell\'{\i}n, Colombia
}

@@

Here we show that the concentration parameter in dark matter halos from
N-body simulations can be reliably estimated from the radially integrated mass
profile.
The main advantage of this method is that it uses the full
particle information without any binning, {\bf which makes it very
  switable in cases when resolution becomes important}. We test our
method both on mock and N-body halos to compare it against two popular
methods to find concentrations: maximum radial velocity measurements
and radial particle binning to {\bf fit the density profile}. Tests on
the mock halos show that the accuracy of our method to recover input
concentrations varies with the halo {\bf resolution}. For halos
sampled with $20$ particles our method recovers the input
concentration with $10\%$ accuracy. {\bf For the maximum radial
  velocity method it is on the order of $20\%$ while density profile
  methods perform worst at the low resolution limit since they require
  at least 200 particles inside the virial radius to make a reliable
  estimate of the density profile}. For halos with $2\times 10^4$
particles our method achieves an accuracy of $0.01\%$ while the
velocity and density profile methods achieve $0.1\%$ and $1\%$,
respectively. We measure the mass-concentration relationship on N-body
data taking care of using halos sampled with at least $200$
particles. We find that at low masses $10^{12}\hMsun <
M<10^{13}\hMsun$ our method yields median concentration values lower
by a $15\%-20\%$ compared to the velocity and density methods ({\bf
  why?}).  At higher masses $3\times 10^{13}\hMsun < M < 2\times
10^{14}\hMsun$ the three methods give similar results.
\end{abstract}
